Sequential Composition for Relaxed Memory: Pomsets with Predicate Transformers

### 2021-02-25 paper/arm.tex
Updated defs

\subsection{Downgraded Reads (\xDGR)}
\label{sec:internal}

@@

\begin{example}
  Revisiting \refex{ex:dgr1} and eliding irrelevant transformers:
  \begin{align*}
    \begin{gathered}[t]
      \PW{x}{2}
      \\
      \hbox{\begin{tikzinline}[node distance=0.5em and 1.5em]
          \event{a}{\DW{x}{2}}{}
          \xform{x1d}{\bForm[\TRUE/\Dx{\aLoc}]}{below=of a}
          % \xform{x1i}{\lnot\Qw{x}\land\bForm[\TRUE/\Dx{x}]}{below=of x1d}
          \xo{a}{x1d}
        \end{tikzinline}}  
    \end{gathered}  
    &&
    \begin{gathered}[t]
      \PR[\mRA]{x}{r}
      \\
      \hbox{\begin{tikzinline}[node distance=0.5em and 1.5em]
          \raevent{b}{\DR[\mRA]{x}{2}}{}
          % \xform{x1d}{2{=}r\limplies\bForm}{below=of b}
          \xform{x1i}{\Dx{x} \land\bForm[\FALSE/\Qr{x}]}{below=of b} %x1d}
          % \xo{b}{x1d}
        \end{tikzinline}}  
    \end{gathered}  
    &&
    \begin{gathered}[t]
      \PW{y}{1}
      \\
      \hbox{\begin{tikzinline}[node distance=0.5em and 1.5em]
          \event{c}{\DW{y}{1}}{}
          % \xform{x1d}{\bForm[\TRUE/\Dx{\aLoc}]}{below=of c}
          % \xform{x1i}{\lnot\Qw{y}\land\bForm[\TRUE/\Dx{y}]}{below=of x1d}
          % \xo{c}{x1d}
        \end{tikzinline}}  
    \end{gathered}  
  \end{align*}
  Associating right:
  \begin{align*}
    \begin{gathered}[t]
      \PW{x}{2}
      \\
      \hbox{\begin{tikzinline}[node distance=0.5em and 1.5em]
          \event{a}{\DW{x}{2}}{}
          \xform{x1d}{\bForm[\TRUE/\Dx{\aLoc}]}{right=.7em of a}
          % \xform{x1i}{\lnot\Qw{x}\land\bForm[\TRUE/\Dx{x}]}{below=of x1d}
          \xo{a}{x1d}
        \end{tikzinline}}  
    \end{gathered}  
    &&
    \begin{gathered}[t]
      \PR[\mRA]{x}{r}
      \SEMI
      \PW{y}{1}
      \\
      \hbox{\begin{tikzinline}[node distance=0.5em and 1.5em]
          \raevent{b}{\DR[\mRA]{x}{2}}{}
          \event{c}{\Dx{x}\mid\DW{y}{1}}{right=.7em of b}
        \end{tikzinline}}  
    \end{gathered}  
  \end{align*}
  Composing, we have, as desired:
  \begin{align*}
    \begin{gathered}[t]
      \PW{x}{2}
      \SEMI
      \PR[\mRA]{x}{r}
      \SEMI
      \PW{y}{1}
      \\
      \hbox{\begin{tikzinline}[node distance=0.5em and 1.5em]
          \event{a}{\DW{x}{2}}{}
          \raevent{b}{\DR[\mRA]{x}{2}}{right=of a}
          \event{c}{\DW{y}{1}}{right=of b}
          \rf{a}{b}
        \end{tikzinline}}  
    \end{gathered}  
  \end{align*}
\end{example}

@@

\begin{definition}[\xRRD]
  \label{def:pomsets-rr}
  Update \refdef{def:pomsets-trans} to:
  \begin{enumerate}
  \item[\ref{T3})]
    $\labelingForm(\aEv)$ implies
    $\labelingForm_1(\aEv)[\TRUE/\RW]$ if $\labelingAct_1(\aEv)$ is a write,
    \\
    $\labelingForm(\aEv)$ implies
    $\labelingForm_1(\aEv)[\FALSE/\RW]$ otherwise.
  \end{enumerate}
  \begin{enumerate}
  \item[\ref{L4})]
    $\aTr{\bEvs}{\bForm}$ implies $\aVal{=}\aReg\limplies\bForm$, 
  \item[\ref{L5})]
    % $\aTr{\cEvs}{\bForm}$ implies $\RW\limplies(\aVal{=}\aReg\lor\aLoc{=}\aReg)\limplies\bForm$,
    $\aTr{\cEvs}{\bForm}$ implies $(\aVal{=}\aReg\lor\RW)\limplies\bForm$,
  \end{enumerate}  
\end{definition}
For reads, the dependent and independent predicate transformers are identical
(since $\RW$ is $\FALSE$).  For writes, \ref{L5} requires
$\aTr{\cEvs}{\bForm}$ implies $\bForm$ for the independent case (since $\RW$
is $\TRUE$).

\begin{example}
  Revisiting \refex{ex:rrd1} and eliding irrelevant transformers:
  \begin{align*}
    \begin{gathered}[t]
      \PR{y}{r}
      \\
      \hbox{\begin{tikzinline}[node distance=0.5em and .5em]
          \event{b}{\DR{y}{1}}{}
          \xform{x1i}{(1{=}r\lor\RW)\limplies\bForm}{right=of b} %x1d}
        \end{tikzinline}}  
    \end{gathered}  
    &&
    \begin{gathered}[t]
      \IF{r}\THEN s\GETS x\FI
      \\
      \hbox{\begin{tikzinline}[node distance=0.5em and 1.5em]
          \event{c}{r\mid\DR{x}{0}}{}
          % \xform{x1d}{\bForm[\TRUE/\Dx{\aLoc}]}{below=of c}
          % \xform{x1i}{\lnot\Qw{y}\land\bForm[\TRUE/\Dx{y}]}{below=of x1d}
          % \xo{c}{x1d}
        \end{tikzinline}}  
    \end{gathered}  
  \end{align*}
  Composing sequentially:
  \begin{align*}
    \begin{gathered}[t]
      \PR{y}{r}
      \SEMI
      \IF{r}\THEN s\GETS x\FI
      \\
      \hbox{\begin{tikzinline}[node distance=0.5em and 1.5em]
          \event{b}{\DR{y}{1}}{}
          \event{c}{(1{=}r\lor\RW)\limplies r\mid\DR{x}{0}}{right=of b}
          %\xform{x1i}{\RW\limplies\bForm}{right=of b} %x1d}
        \end{tikzinline}}  
    \end{gathered}  
  \end{align*}
  Embedding the thread in thread group, \ref{T3} yields:
  \begin{align*}
    \begin{gathered}[t]
      % \PR{y}{r}
      % \SEMI
      % \IF{r}\THEN s\GETS x\FI
      % \\
      \hbox{\begin{tikzinline}[node distance=0.5em and 1.5em]
          \event{b}{\DR{y}{1}}{}
          \event{c}{(1{=}r\lor\FALSE)\limplies r\mid\DR{x}{0}}{right=of b}
          %\xform{x1i}{\RW\limplies\bForm}{right=of b} %x1d}
        \end{tikzinline}}  
    \end{gathered}  
  \end{align*}
  The precondition of $\DRP{x}{0}$ is a tautology, as required.
\end{example}

@@

\begin{definition}[\xCO/\xRASC/\xDGR/\xRRD]
  \label{def:pomsets-arm}
  Let $[\aForm/\Q{}]$ be the substitution $[\aForm/\Qr{*}][\aForm/\Qw{*}][\aForm/\Qsc]$.  
  Update \refdef{def:pomsets-trans} to: % (\ref{L4} unchanged):
  \begin{enumerate}
  \item[\ref{S3})]
    $\labelingForm(\aEv)$ implies $\QS{\aLoc}{\amode}\land\aExp{=}\aVal$,
  \item[\ref{L3})]
    $\labelingForm(\aEv)$ implies $\QL{\aLoc}{\amode}$.
  \item[\ref{T3})]
    $\labelingForm(\aEv)$ implies
    $\labelingForm_1(\aEv)[\TRUE/\Q{}][\TRUE/\RW]$ if $\labelingAct_1(\aEv)$ is a write,
    \\
    $\labelingForm(\aEv)$ implies
    $\labelingForm_1(\aEv)[\TRUE/\Q{}][\FALSE/\RW]$ otherwise.
  \end{enumerate}
  \begin{enumerate}
  \item[\ref{S4})]
    $\aTr{\bEvs}{\bForm}$ implies
    \begin{math}
      %(\Qw{\aLoc}\limplies\aExp{\neq}\aVal)\land
      \bForm %\noSUB{[\aExp/\aLoc]},
      [(\Qw{\aLoc}\land\aExp{=}\aVal)/\Qw{\aLoc}]
      \DS{\aLoc}{\amode}
    \end{math}
  \item[\ref{S5})]
    $\aTr{\cEvs}{\bForm}$ implies
    \begin{math}
      %\lnot\Qw{\aLoc}\land 
      \bForm %\noSUB{[\aExp/\aLoc]}.
      [\FALSE/\QS{\aLoc}{\amode}]
      \DS{\aLoc}{\amode}
    \end{math}
  \item[\ref{L4})]
    $\aTr{\bEvs}{\bForm}$ implies $\aVal{=}\aReg\limplies\bForm$, 
  \item[\ref{L5})]
    % $\aTr{\cEvs}{\bForm}$ implies $\lnot\Qx{\aLoc} \land \DL{\aLoc}{\amode} \land(\RW\limplies(\aVal{=}\aReg\lor\aLoc{=}\aReg)\limplies\bForm)$,
    % \item[\ref{L6})]
    $\aTr{\cEvs}{\bForm}$ implies
    \begin{math}
      % \lnot\Qx{\aLoc} \land
      \DL{\aLoc}{\amode}{} \land (\RW\limplies\bForm[\FALSE/\QL{\aLoc}{\amode}]).
    \end{math}
  \end{enumerate}  
\end{definition}

\begin{example}
  \xRRD{} does not adversely affect subscription (\refex{ex:subscription}).
  \begin{align*}
    \begin{gathered}[t]
      \PR[\mRA]{y}{r}
      \\
      \hbox{\begin{tikzinline}[node distance=0.5em and .5em]
          \raevent{b}{\QL{y}{\mRA}\mid\DR[\mRA]{y}{1}}{}
          \xform{x1i}{\Dx{y}\land(\RW\limplies\bForm[\FALSE/\QL{\aLoc}{\mRA}])}{right=of b} %x1d}
        \end{tikzinline}}  
    \end{gathered}  
    &&
    \begin{gathered}[t]
      \PR{x}{s}
      \\
      \hbox{\begin{tikzinline}[node distance=0.5em and 1.5em]
          \event{c}{\QL{y}{\mRA}\mid\DW{x}{0}}{}
        \end{tikzinline}}  
    \end{gathered}  
  \end{align*}
  Since $\QL{y}{\mRA}[\FALSE/\QL{\aLoc}{\mRA}]$ is false, we have:
  \begin{align*}
    \begin{gathered}[t]
      \PR[\mRA]{y}{r}
      \SEMI
      \PR{x}{s}
      \\
      \hbox{\begin{tikzinline}[node distance=0.5em and 1.5em]
          \raevent{b}{\QL{y}{\mRA}\mid\DR[\mRA]{y}{1}}{}
          \event{c}{\Dx{y}\land(\RW\limplies\FALSE)\mid\DW{x}{0}}{right=of b}
        \end{tikzinline}}  
    \end{gathered}  
  \end{align*}
  If this is the complete thread, we apply \ref{T3} to yield:
  \begin{align*}
    \begin{gathered}[t]
      % \PR[\mRA]{y}{r}
      % \SEMI
      % \PR{x}{s}
      % \\
      \hbox{\begin{tikzinline}[node distance=0.5em and 1.5em]
          \raevent{b}{\QL{y}{\mRA}\mid\DR[\mRA]{y}{1}}{}
          \event{c}{\Dx{y}\land(\FALSE\limplies\FALSE)\mid\DW{x}{0}}{right=of b}
        \end{tikzinline}}  
    \end{gathered}  
  \end{align*}
  Although $(\FALSE\limplies\FALSE)$ is a tautology, $\Dx{y}$ is not.  This
  pomset can only contribute to a top-level pomset if the thread is preceded
  by a relaxed write to $y$, allowing $\DRP[\mRA]{y}{1}$ to be downgraded to
  a relaxed read.
\end{example}

>>>>

\subsection{Downgraded Reads (\xDGR)}
\label{sec:downgrade}

@@

\begin{example}
  Revisiting \refex{ex:dgr1} and eliding irrelevant transformers:
  \begin{align*}
    \begin{gathered}[t]
      \PW{x}{2}
      \\
      \hbox{\begin{tikzinline}[node distance=0.5em and 1.5em]
          \event{a}{\DW{x}{2}}{}
          \xform{x1d}{\bForm[\TRUE/\Dx{\aLoc}]}{below=of a}
          % \xform{x1i}{\lnot\Qw{x}\land\bForm[\TRUE/\Dx{x}]}{below=of x1d}
          \xo{a}{x1d}
        \end{tikzinline}}  
    \end{gathered}  
    &&
    \begin{gathered}[t]
      \PR[\mRA]{x}{r}
      \\
      \hbox{\begin{tikzinline}[node distance=0.5em and 1.5em]
          \raevent{b}{\DR[\mRA]{x}{2}}{}
          % \xform{x1d}{2{=}r\limplies\bForm}{below=of b}
          \xform{x1i}{\Dx{x} \land\bForm[\FALSE/\Qr{x}]}{below=of b} %x1d}
          % \xo{b}{x1d}
        \end{tikzinline}}  
    \end{gathered}  
    &&
    \begin{gathered}[t]
      \PW{y}{1}
      \\
      \hbox{\begin{tikzinline}[node distance=0.5em and 1.5em]
          \event{c}{\DW{y}{1}}{}
          % \xform{x1d}{\bForm[\TRUE/\Dx{\aLoc}]}{below=of c}
          % \xform{x1i}{\lnot\Qw{y}\land\bForm[\TRUE/\Dx{y}]}{below=of x1d}
          % \xo{c}{x1d}
        \end{tikzinline}}  
    \end{gathered}  
  \end{align*}
  Associating right:
  \begin{align*}
    \begin{gathered}[t]
      \PW{x}{2}
      \\
      \hbox{\begin{tikzinline}[node distance=0.5em and 1.5em]
          \event{a}{\DW{x}{2}}{}
          \xform{x1d}{\bForm[\TRUE/\Dx{\aLoc}]}{right=.7em of a}
          % \xform{x1i}{\lnot\Qw{x}\land\bForm[\TRUE/\Dx{x}]}{below=of x1d}
          \xos{a}{x1d}
        \end{tikzinline}}  
    \end{gathered}  
    &&
    \begin{gathered}[t]
      \PR[\mRA]{x}{r}
      \SEMI
      \PW{y}{1}
      \\
      \hbox{\begin{tikzinline}[node distance=0.5em and 1.5em]
          \raevent{b}{\DR[\mRA]{x}{2}}{}
          \event{c}{\Dx{x}\mid\DW{y}{1}}{right=.7em of b}
        \end{tikzinline}}  
    \end{gathered}  
  \end{align*}
  Composing, we have, as desired:
  \begin{align*}
    \begin{gathered}[t]
      \PW{x}{2}
      \SEMI
      \PR[\mRA]{x}{r}
      \SEMI
      \PW{y}{1}
      \\
      \hbox{\begin{tikzinline}[node distance=0.5em and 1.5em]
          \event{a}{\DW{x}{2}}{}
          \raevent{b}{\DR[\mRA]{x}{2}}{right=of a}
          \event{c}{\DW{y}{1}}{right=of b}
          \rf{a}{b}
        \end{tikzinline}}  
    \end{gathered}  
  \end{align*}
\end{example}

@@

\begin{definition}[\xRRD]
  \label{def:pomsets-rr}
  Update \refdef{def:pomsets-trans} to:
  % \begin{enumerate}
  % \item[\ref{T3})]
  %   $\labelingForm(\aEv)$ implies
  %   $\labelingForm_1(\aEv)[\TRUE/\RW]$ if $\labelingAct_1(\aEv)$ is a write,
  %   \\
  %   $\labelingForm(\aEv)$ implies
  %   $\labelingForm_1(\aEv)[\FALSE/\RW]$ otherwise.
  % \end{enumerate}
  \begin{enumerate}
  \item[\ref{L4})]
    $\aTr{\bEvs}{\bForm}$ implies $\aVal{=}\aReg\limplies\bForm$, 
  \item[\ref{L5})]
    % $\aTr{\cEvs}{\bForm}$ implies $\RW\limplies(\aVal{=}\aReg\lor\aLoc{=}\aReg)\limplies\bForm$,
    $\aTr{\cEvs}{\bForm}$ implies $(\aVal{=}\aReg\lor\RW)\limplies\bForm$, when $\aEvs\neq\emptyset$,
  \item[{\labeltext[L6]{L6)}{L6}}] 
    $\aTr{\dEvs}{\bForm}$ implies $\bForm$, when $\aEvs=\emptyset$.
  \end{enumerate}  
\end{definition}
\ref{L4} is the \emph{dependent} case,
\ref{L5} the \emph{independent} case, and
\ref{L6} the \emph{empty} case. 
 Recall the substitutions performed by $\ref{sTOP}$
(\refdef{def:pomsets-top}).
For writes, \ref{L5} is the same as \ref{L6} (since $\RW$
is $\TRUE$).  For reads, \ref{L5} is the
same as \ref{L4} (since $\RW$ is $\FALSE$).
% For reads, the dependent and independent predicate transformers are identical
% .  For writes, \ref{L5} requires
% $\aTr{\cEvs}{\bForm}$ implies $\bForm$ for the independent case.

One reading of \ref{L5} is that when satisfying a precondition $\aForm$ it is
safe to use the value of the read, as long as the action is not a write.  If
the pomset is empty, however, there is no value $\aVal$ to use.  Therefore
the best we can do is to emulate skip, as in \ref{L6}.  % In order to
% eventually arrive at a top-level pomset, this means that subsequent code must
% be independent of $\aReg$.

\begin{example}
  Revisiting \refex{ex:rrd1} and eliding irrelevant transformers:
  \begin{align*}
    \begin{gathered}[t]
      \PR{y}{r}
      \\
      \hbox{\begin{tikzinline}[node distance=0.5em and .5em]
          \event{b}{\DR{y}{1}}{}
          \xform{x1i}{(1{=}r\lor\RW)\limplies\bForm}{right=of b} %x1d}
        \end{tikzinline}}  
    \end{gathered}  
    &&
    \begin{gathered}[t]
      \IF{r}\THEN s\GETS x\FI
      \\
      \hbox{\begin{tikzinline}[node distance=0.5em and 1.5em]
          \event{c}{r\mid\DR{x}{0}}{}
          % \xform{x1d}{\bForm[\TRUE/\Dx{\aLoc}]}{below=of c}
          % \xform{x1i}{\lnot\Qw{y}\land\bForm[\TRUE/\Dx{y}]}{below=of x1d}
          % \xo{c}{x1d}
        \end{tikzinline}}  
    \end{gathered}  
  \end{align*}
  Composing sequentially:
  \begin{align*}
    \begin{gathered}[t]
      \PR{y}{r}
      \SEMI
      \IF{r}\THEN s\GETS x\FI
      \\
      \hbox{\begin{tikzinline}[node distance=0.5em and 1.5em]
          \event{b}{\DR{y}{1}}{}
          \event{c}{(1{=}r\lor\RW)\limplies r\mid\DR{x}{0}}{right=of b}
          %\xform{x1i}{\RW\limplies\bForm}{right=of b} %x1d}
        \end{tikzinline}}  
    \end{gathered}  
  \end{align*}
  At top-level, $\ref{sTOP}$ yields:
  \begin{align*}
    \begin{gathered}[t]
      % \PR{y}{r}
      % \SEMI
      % \IF{r}\THEN s\GETS x\FI
      % \\
      \hbox{\begin{tikzinline}[node distance=0.5em and 1.5em]
          \event{b}{\DR{y}{1}}{}
          \event{c}{(1{=}r\lor\FALSE)\limplies r\mid\DR{x}{0}}{right=of b}
          %\xform{x1i}{\RW\limplies\bForm}{right=of b} %x1d}
        \end{tikzinline}}  
    \end{gathered}  
  \end{align*}
  The precondition of $\DRP{x}{0}$ is a tautology, as required.
\end{example}

@@

\begin{definition}[\xCO/\xRASC/\xDGR/\xRRD]
  \label{def:pomsets-arm}
  Let $[\aForm/\Q{}]$ be the substitution $[\aForm/\Qr{*}][\aForm/\Qw{*}][\aForm/\Qsc]$.  
  Update \refdef{def:pomsets-trans} to: % (\ref{L4} unchanged):
  \begin{enumerate}
  \item[\ref{S3})]
    $\labelingForm(\aEv)$ implies $\QS{\aLoc}{\amode}\land\aExp{=}\aVal$,
  \item[\ref{L3})]
    $\labelingForm(\aEv)$ implies $\QL{\aLoc}{\amode}$.
  % \item[\ref{T3})]
  %   $\labelingForm(\aEv)$ implies
  %   $\labelingForm_1(\aEv)[\TRUE/\Q{}][\TRUE/\RW]$ if $\labelingAct_1(\aEv)$ is a write,
  %   \\
  %   $\labelingForm(\aEv)$ implies
  %   $\labelingForm_1(\aEv)[\TRUE/\Q{}][\FALSE/\RW]$ otherwise.
  \end{enumerate}
  \begin{enumerate}
  \item[\ref{S4})]
    $\aTr{\bEvs}{\bForm}$ implies
    \begin{math}
      %(\Qw{\aLoc}\limplies\aExp{\neq}\aVal)\land
      \bForm %\noSUB{[\aExp/\aLoc]},
      [(\Qw{\aLoc}\land\aExp{=}\aVal)/\Qw{\aLoc}]
      \DS{\aLoc}{\amode}
    \end{math}
  \item[\ref{S5})]
    $\aTr{\cEvs}{\bForm}$ implies
    \begin{math}
      %\lnot\Qw{\aLoc}\land 
      \bForm %\noSUB{[\aExp/\aLoc]}.
      [\FALSE/\QS{\aLoc}{\amode}]
      \DS{\aLoc}{\amode}
    \end{math}
  \item[\ref{L4})]
    $\aTr{\bEvs}{\bForm}$ implies $\aVal{=}\aReg\limplies\bForm$, 
  \item[\ref{L5})]
    % $\aTr{\cEvs}{\bForm}$ implies $\lnot\Qx{\aLoc} \land \DL{\aLoc}{\amode} \land(\RW\limplies(\aVal{=}\aReg\lor\aLoc{=}\aReg)\limplies\bForm)$,
    % \item[\ref{L6})]
    $\aTr{\cEvs}{\bForm}$ implies
    \begin{math}
      % \lnot\Qx{\aLoc} \land
      \DL{\aLoc}{\amode}{} \land ((\aVal{=}\aReg\lor\RW)\limplies\bForm[\FALSE/\QL{\aLoc}{\amode}]).
    \end{math}
  \end{enumerate}  
\end{definition}

\begin{example}
  \xRRD{} does not adversely affect subscription (\refex{ex:subscription}).
  \begin{align*}
    \begin{gathered}[t]
      \PR[\mRA]{y}{r}
      \\
      \hbox{\begin{tikzinline}[node distance=0.5em and .5em]
          \raevent{b}{\QL{y}{\mRA}\mid\DR[\mRA]{y}{1}}{}
          \xform{x1i}{\Dx{y}\land(\RW\limplies\bForm[\FALSE/\QL{\aLoc}{\mRA}])}{right=of b} %x1d}
        \end{tikzinline}}  
    \end{gathered}  
    &&
    \begin{gathered}[t]
      \PR{x}{s}
      \\
      \hbox{\begin{tikzinline}[node distance=0.5em and 1.5em]
          \event{c}{\QL{y}{\mRA}\mid\DW{x}{0}}{}
        \end{tikzinline}}  
    \end{gathered}  
  \end{align*}
  Since $\QL{y}{\mRA}[\FALSE/\QL{\aLoc}{\mRA}]$ is false, we have:
  \begin{align*}
    \begin{gathered}[t]
      \PR[\mRA]{y}{r}
      \SEMI
      \PR{x}{s}
      \\
      \hbox{\begin{tikzinline}[node distance=0.5em and 1.5em]
          \raevent{b}{\QL{y}{\mRA}\mid\DR[\mRA]{y}{1}}{}
          \event{c}{\Dx{y}\land(\RW\limplies\FALSE)\mid\DW{x}{0}}{right=of b}
        \end{tikzinline}}  
    \end{gathered}  
  \end{align*}
  Applying $\ref{sTOP}$ yields:
  \begin{align*}
    \begin{gathered}[t]
      % \PR[\mRA]{y}{r}
      % \SEMI
      % \PR{x}{s}
      % \\
      \hbox{\begin{tikzinline}[node distance=0.5em and 1.5em]
          \raevent{b}{\TRUE\mid\DR[\mRA]{y}{1}}{}
          \event{c}{\Dx{y}\land(\FALSE\limplies\FALSE)\mid\DW{x}{0}}{right=of b}
        \end{tikzinline}}  
    \end{gathered}  
  \end{align*}
  Although $(\FALSE\limplies\FALSE)$ is a tautology, $\Dx{y}$ is not.  Thus,
  the pomset can only contribute to a top-level pomset if the thread is
  preceded by a relaxed write to $y$, allowing $\DRP[\mRA]{y}{1}$ to be
  downgraded to a relaxed read.
\end{example}

### 2021-02-25 paper/outro.tex
Minor edits
Updated defs

For sequential composition, parallel composition and the conditional, we
believe that the definition is \emph{natural}, even \emph{canonical}.
For stores and loads, instead, the definition in \reffig{fig:full} is a
Frankenstein's monster of features.  This complexity is \emph{essential},
however, not just an accident of our poor choices.  Relaxed memory models must
please many audiences: compiler writers want one thing, hardware designers
another, and programmers yet another still.  The result is inevitably full of
compromise.

Given that \emph{complexity} cannot be eliminated from relaxed memory models,
the best one can do is attempt to understand its causes.  We have broken the
problem into eight manageable pieces, discussed throughout
\textsection\ref{sec:q}--\ref{sec:complications}.  \refdef{def:pomsets-arm}
summarizes all the features necessary for efficient implementation on
\armeight{}.

>>>>

For sequential composition, parallel composition and the conditional, we
believe that the definition is \emph{natural}, even \emph{canonical}.
For stores and loads, instead, the definition in \reffig{fig:no-addr} is a
Frankenstein's monster of features.  This complexity is \emph{essential},
however, not just an accident of our poor choices.  Relaxed memory models must
please many audiences: compiler writers want one thing, hardware designers
another, and programmers yet another still.  The result is inevitably full of
compromise.

Given that \emph{complexity} cannot be eliminated from relaxed memory models,
the best one can do is attempt to understand its causes.  We have broken the
problem into seven manageable pieces, discussed throughout
\textsection\ref{sec:q}--\ref{sec:complications}.  \refdef{def:pomsets-arm}
summarizes all the features necessary for efficient implementation on
\armeight{}.  We discuss address calculation, read-modify-write operations
and fences in the appendix.
